|

### 2019-09-14 paper.Rmd
r, R and epsilon need to be defined

\noindent and $\mathbf{x}_i, i=1,...,n$ a $p$-dimensional observation in $\mathbf{X}$ and $\mathbf{a}_i, i=1,2$ denoting the columns of the projection matrix, $\mathbf{A}=(\mathbf{a}_1, \mathbf{a}_2)$.
Calculating the euclidean norm of $\mathbf{x}'$ is straightforward thanks to the orthonormality of $\mathbf{A}$, and gives the components of the required distance vector. This can be generalized for $d>2$.

@@

Choosing the slice thickness is a compromise between what feature size can be resolved and how many points fall inside a thin slice. As dimensionality $p$ increases, the relative number of points that are inside a slice of fixed thickness $h$ will decrease. The exact relation depends on the distribution of the data points. Here we estimate how it scales with $h$ and $p$ for the example of points uniformly distributed in a hypersphere. The example was selected since it represents a rotation invariant uniform distribution in $p$ space. As we are interested in hollowness this type of distribution is more relevant than a multivariate normal distribution.

The fraction of points inside a slice of thickness $h$ can be estimated as the relative volume of the slice compared to the volume of the full hypersphere,
\begin{equation}
V_{rel} = \frac{1}{2} \frac{h^{p-2}}{r^p} (p r^2 - (p-2) h^2) \approx \frac{1}{2} (\frac{h}{R})^{p-2},
\end{equation}
where the approximation is valid when $h \ll r$, as is typically expected to be the case. Thus if we want to keep the relative number of points (i.e. $V_{rel}$) approximately constant for slices in different dimensions $p$, we calculate $h$ from a volume parameter as $h = \epsilon^{1/(p-2)}$.

>>>>

\noindent and $\mathbf{x}_i, i=1,...,n$ is a $p$-dimensional observation in $\mathbf{X}$ and $\mathbf{a}_i, i=1,2$ denoting the columns of the projection matrix, $\mathbf{A}=(\mathbf{a}_1, \mathbf{a}_2)$.
Calculating the euclidean norm of $\mathbf{x}'$ is straightforward thanks to the orthonormality of $\mathbf{A}$, and gives the components of the required distance vector. This can be generalized for $d>2$.

@@

Choosing the slice thickness is a compromise between what feature size can be resolved and the sparseness of the data. As $p$ increases, the relative number of points that are inside a slice of fixed thickness $h$ will decrease. The exact relation depends on the distribution of the data points. To get a best estimate for $h$, given $p$, assume that the points are uniformly distributed in a hypersphere. This is a rotation invariant uniform distribution in $p$ space, and because with sllicing we are mostly interested in hollowness this is more relevant than assuming a multivariate normal distribution.

The fraction of points inside a slice of thickness $h$ can be estimated as the relative volume of the slice compared to the volume of the full hypersphere,
\begin{equation}
V_{rel} = \frac{1}{2} \frac{h^{p-2}}{r^p} (p r^2 - (p-2) h^2) \approx \frac{1}{2} (\frac{h}{R})^{p-2},
\end{equation}
where $r$ is XXX, and $R$ is XXX. The approximation is valid when $h \ll r$, as is typically expected to be the case. To keep the relative number of points (i.e. $V_{rel}$) approximately constant for slices in different dimensions $p$, we calculate $h$ from a volume parameter as $h = \epsilon^{1/(p-2)}$, where $epsilon$ is XXX.
